---
title: "What does data tell us about the education situations around the world?"
author:
- familyname: YANG
  othernames: Mengyuan
  address: Monash University
  email: "myan0065@student.monash.edu"
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: BATSAIKHAN
  othernames: Zoljargal
  address: Monash University
  email: "zbat0001@student.monash.edu"
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: WANG
  othernames: Xinrui
  address: Monash University
  email: "xwan0274@student.monash.edu"
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: GOH
  othernames: Xueqi
  address: MONASH UNIVERSITY
  email: "xgoh0002@student.monash.edu"
  correspondingauthor: true
  qualifications: Master of Business Analytics
department: Our consultancy \newline Mengyuan YANG &\newline Zoljargal BATSAIKHAN &\newline Xinrui WANG &\newline Xueqi GOH
organization: Monash University
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: true
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(ggplot2)
library(gridExtra)
library(tinytex)
library(readxl)
library(naniar)
```


\section*{Introduction}

```{r}
excel_sheets("data/API_4_DS2_en_excel_v2_2252569.xls")

data_income <- read_excel("data/CLASS.xls", range = anchored("C5", dim = c(220,5))) %>% 
  select(-X) %>% 
  filter(Economy != "x")
```

```{r}
df<- read_excel("Data/API_4_DS2_en_excel_v2_2252569.xls", sheet = 1, range = "A4:BM42772") %>% 
  select("Country Name", 
         "Country Code",
         "Indicator Name", 
         "2000":"2019") %>% 
  rename("country_name" = "Country Name",
         "indicator" = "Indicator Name",
         "country_code" = "Country Code")
```


```{r}
df %>%
  group_by(country_name) %>%
  miss_var_summary() %>% 
  arrange(-pct_miss)
```

```{r}
df_filter <- df %>% 
  filter(!(country_name %in% c("Faroe Islands",
                          "Greenland",
                          "Isle of Man",
                          "Not classified",
                          "St. Martin (French part)",
                          "Northern Mariana Islands",
                          "Kosovo",
                          "American Samoa",
                          "Gibraltar",
                          "Sint Maarten (Dutch part)",
                          "Turks and Caicos Islands",
                          "Channel Islands",
                          "Guam",
                          "French Polynesia",
                          "Curacao",
                          "New Caledonia",
                          "Virgin Islands (U.S.)",
                          "Nauru",
                          "Palau",
                          "Somalia",
                          "Guinea-Bissau")))
       
```

```{r}
data_joined <- df_filter %>% 
    left_join(data_income, by = c("country_name" = "Economy",
                                "country_code" = "Code")) 
```

\section*{Mengyun}


\section*{Zoljargal}


\section*{Percentage of children out of primary school}

This section discusses the percentage of primary-school-age children who are not enrolled in primary or secondary school across regions between 2000 to 2019, including the changes of overall percentage and the difference in percentage between gender over these two decades. 

```{r}
df_outsch <- data_joined %>% 
  filter(indicator %in% c("Children out of school (% of primary school age)",
                          "Children out of school, male (% of male primary school age)",
                          "Children out of school, female (% of female primary school age)")) %>% 
  pivot_longer(cols = "2000":"2019",
               names_to = "year",
               values_to = "value") %>% 
  pivot_wider(id_cols = -indicator,
              names_from = indicator,
              values_from = value) %>% 
  rename("children_out_of_school_tot_%" = `Children out of school (% of primary school age)`,
         "children_out_of_school_m_%" = `Children out of school, male (% of male primary school age)`,
         "children_out_of_school_f_%" = `Children out of school, female (% of female primary school age)`)
```

```{r}
outsch <- df_outsch %>% 
  filter(country_name %in% c("East Asia & Pacific",
                             "Europe & Central Asia",
                             "Latin America & Caribbean",
                             "Middle East & North Africa",
                             "North America",
                             "South Asia",
                             "Sub-Saharan Africa")) 

```

```{r}
income_level <- data_income %>% 
  select(Region,`Income group`)
```

```{r}
os_clean <- outsch %>% 
  left_join(income_level,
            by = c("country_name" = "Region")) %>% 
  select(-c(country_code, Region, `Income group.x`)) %>% 
  rename("region" = country_name,
         "income_group" = `Income group.y`) %>% 
  mutate(year = as.numeric(year))

os_clean <- unique(os_clean[ , 1:5])
```

Figure \@ref(fig:plot1xw) shows that among all of the seven regions, Sub-Saharan Africa has the highest percentage of primary-school-age children out of school, followed by South Asia and Middle East & North Africa. However, all of these three countries witnessed a decrease in the percentage, especially in Sub-Saharan Africa, the figure dropped from nearly 40% in 2000 to lower than 20% in 2019. As suggested by @bennell2002hitting, high levels of sustained enrollment growth could be observed in Sub-Sahara Africa between 2000 and 2015. The percentage in South Asia and Middle East & North Africa also decreased to below 10% in 2019 while the figure for rest regions remained relatively steady between 0-5%.

```{r plot1xw, fig.cap="Percentage of children out of school in primary school age"}
os_clean %>% 
  ggplot(aes(x = year, y = `children_out_of_school_tot_%`, colour = region)) +
  geom_line() +
  labs(x = "Year", y = "Percentage") +
  scale_fill_brewer(palette="Paired") +
  theme_light() 
```

```{r}
os_gender <- os_clean %>% 
  rename("male" = `children_out_of_school_m_%`,
         "female" = `children_out_of_school_f_%`) %>% 
  pivot_longer(cols = c(male,female),
               names_to = "gender",
               values_to = "percentage") %>% 
  select(-`children_out_of_school_tot_%`)
```

To have a deeper understanding, Figure \@ref(fig:plot1xw) explores the difference of percentage of primary-school-age out of school in gender across regions. Again, in Middle East & North Africa, South Asia and Sub-Saharan Africa, where the total percentage is significantly higher, it is obvious that more females in primary school age are out of school compare with males.

```{r plot2xw, fig.cap="Percentage of children out of school in primary school age by gender", warning=FALSE}
os_gender %>% 
ggplot(aes(x= year, y = percentage, fill = gender)) +
  facet_wrap(~region,
             ncol = 2) +
  geom_bar(stat = "identity",
           position = "dodge") +
  xlim(c(2000,2019)) +
  labs(x = "Year", y = "Percentage") +
  scale_fill_brewer(palette="Paired") +
  theme_light() 
```

```{r}
os_diff <- os_clean %>% 
  filter(year %in% c(2000,2019)) %>% 
  group_by(region, year) %>% 
  summarise(per_diff = `children_out_of_school_f_%` - `children_out_of_school_m_%`,
            .groups = "drop") %>% 
  pivot_wider(names_from = year,
              values_from = per_diff)
```

According to Table \@ref(tab:tb1xw), in South Asia, the difference in percentage between male and female was the highest in 2000, the percentage of female children out of primary school is 13.05% higher than male. However, the difference decreased along with the total percentage, by the year of 2019, the difference in percentage has dropped to 1.26%. 

Same changes can be observed in Middle East & North Africa, the difference in percentage also decreased from 7.33% to 1.94% between 2000 and 2019. Whereas in Sub-Saharan Africa, even though the total percentage drooped over the years, the difference in percentage between male and female school aged children did not decrease as much as in South Asia and Middle East & North Africa. In 2019, the percentage of female children out of primary school is still 4.29% higher compare with male.

```{r tb1xw}
os_diff[order(-os_diff$`2000`),] %>% 
  kable(col.names = c("Region", 
                      "Difference in percentage - 2000",
                      "Difference in percentage - 2019"),
      align = "c",
      caption = "Difference in percentage of primary-school-age children out of school between males and females", 
      digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped","hover"),
                latex_options = "HOLD_position")
```

Another interesting finding is that in Europe & Central Asia and Latin America & Caribbean, the difference in percentage is -0.14% and -0.56% respectively in 2019, which indicates that in 2019, the percentage of primary-school-age male who are not enrolled in primary or secondary school is actually slightly higher than female, although the difference is very close to zero (Table \@ref(tab:tb1xw)).


\section*{Xueqi}


\section*{Conclusion}

